Tor's Usability for Censorship Circumvention

### 2015-10-09 paper/circumvention-experiment.tex
added more writing and screenshots of the configuration interface

\noindent {\bfseries Overview}
The Tor Browser provides a configuration interface (Figure
~\ref{fig:bridges}) to guide users through setting up their connection to the
Tor network. While people in most countries can connect to Tor using the
dialog's default settings, citizens in certain censorship environments must
make use of additional settings, such as bridges, proxies, or both. 
%definition of a bridge, defintion of a proxy here. 
Our study  will explore how well this interface successfully guides users to 
correctly configuring their browser.\\

@@

\noindent {\bfseries Configuration Flow}
{\color {red}

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item {\bfseries Path 1}:  Configure directly
\item {\bfseries Path 2}:  Bridge, no proxy
\item {\bfseries Path 3}:  Bridge, proxy 
\item {\bfseries Path 4}:  No bridge, proxy
\item {\bfseries Path 5}:  No bridge, no proxy
\end{itemize}

@@

If a user is not connecting directly to the Tor network, then they are asked to 
configure a bridge (as seen in TODO, the title of the window during configuration 
is ``Tor Bridges Configuration''). We suspect that the reason for configuring a bridge
first before a proxy is that more people need to configure bridges than proxies,
but this is not known. The bridge configuration asks the users if their ISP blocks
or censors connections to the Tor Network. The assumption here is that users will 
not know if they need a bridge or not, but that they are equipped to answer if their
current network environment censors the Tor Network. The configuration interface 
uses this answer to deem if the user needs a bridge. A yes to this question would
require a bridge while a no to this question would not. If they answer yes, they are 
asked to configure the bridges. If they answer no, then the configuration interface 
moves on to configuring proxies.

If a user who is not directly connecting to the Tor network is finished configuring
a bridge or has answered that they do not need a bridge, they are asked to 
configure a local proxy (as seen in TODO, the title of the window during
configuration is ``Local Proxy Configuration''). The proxy configuration asks the 
users if they need to use a local proxy to access the Internet. The assumption 
is that people will not know the answer to this question, so there is a text instructing
users how to find the answer to this question below the question. If the answer to
the question is yes, the user needs a proxy and is taken to a screen where they are
asked to configure the proxy settings. If the user does not need a proxy, then the 
configuration interface attempts to connect to the Tor network with all the 
given inputs up to this point so far.

@@

}

\noindent {\bfseries Things that are good} %% fix this so it's not so casual
{\color {red} 
Talking to users, ``this will work in most situations,'' help button, support email.
putting the bridge configuration before the proxy, etc.... \\
}

\noindent {\bfseries Things that could be improved}%% fix this so it's not so casual
{\color {red} 
clarify between bridges and proxy, getting rid of redundant text, etc.  \\
}

@@

\bibliographystyle{abbrv}
\bibliography{circumvention-experiment.bib} 
\end{document}

>>>>

\noindent {\bfseries Overview}
The Tor Browser provides a configuration interface to guide users through setting up 
their connection to the
Tor network. While people in most countries can connect to Tor using the
dialog's default settings, citizens in certain censorship environments must
make use of additional settings, such as bridges, proxies, or both. 
{\color {red} definition of a bridge, definition of a proxy}   %%%
Our study  will explore how well this interface successfully guides users to 
correctly configuring their browser.\\

@@

\noindent {\bfseries Configuration Flow}
There are five general paths a user can take through the Tor Browser connection
configuration interface. {\color {red} These paths are shown in Figure ~\ref{fig:interface}}. 
The configuration interface asks a series of questions to 
the user to determine if the user requires a bridge or proxy when connecting to 
the Tor network. Depending on how the user answers these questions, a user 
has give paths through the configuration, as follows:

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item {\bfseries Path 1}:  Connect directly
\item {\bfseries Path 2}:  Yes bridge, no proxy, connect
\item {\bfseries Path 3}:  Yes bridge, yes proxy, connect 
\item {\bfseries Path 4}:  No bridge, yes proxy, connect 
\item {\bfseries Path 5}:  No bridge, no proxy, connect 
\end{itemize}

@@

If a user is not connecting directly to the Tor network, then they are asked to 
configure a bridge (as seen in {\color {red} TODO}, the title of the window during configuration %%%
is ``Tor Bridges Configuration''). We suspect that the reason for configuring a bridge
first before a proxy is that more people need to configure bridges than proxies,
but this is not known. The bridge configuration asks the users if their ISP blocks
or censors connections to the Tor Network. The assumption here is that users will 
not know if they need a bridge or not, but that they are equipped to answer if their
current network environment censors the Tor Network. The configuration interface 
uses this answer to deem if the user needs a bridge. A yes to this question would
require a bridge while a no to this question would not. If they answer yes, they are 
asked to configure the bridges. If they answer no, then the configuration interface 
moves on to configuring proxies.

If a user who is not directly connecting to the Tor network is finished configuring
a bridge or has answered that they do not need a bridge, they are asked to 
configure a local proxy (as seen in {\color {red} TODO}, the title of the window during %%%
configuration is ``Local Proxy Configuration''). The proxy configuration asks the 
users if they need to use a local proxy to access the Internet. The assumption 
is that people will not know the answer to this question, so there is a text instructing
users how to find the answer to this question below the question. If the answer to
the question is yes, the user needs a proxy and is taken to a screen where they are
asked to configure the proxy settings. If the user does not need a proxy, then the 
configuration interface attempts to connect to the Tor network with all the 
given inputs up to this point so far.

@@

\noindent {\bfseries Things that are good about the interface} %% fix this so it's not so casual
{\color {red} 
Talking to users, ``this will work in most situations,'' help button, support email.
putting the bridge configuration before the proxy, etc.... \\
}

\noindent {\bfseries Things that could be improved about the interface }%% fix this so it's not so casual
{\color {red} 
clarify between bridges and proxy, getting rid of redundant text, etc.  \\
}

@@

\bibliographystyle{abbrv}
\bibliography{circumvention-experiment.bib}

\appendix
\section*{A1: Configuration Interface Windows}

\begin{figure}[h]
\label{fig:window1}
  \centering
    \includegraphics[width=0.5\textwidth]{window1.png}
    \caption{window1}
\end{figure}

\begin{figure}[h]
\label{fig:window2}
  \centering
    \includegraphics[width=0.5\textwidth]{window2.png}
    \caption{window2}
\end{figure}

\begin{figure}[h]
\label{fig:window3}
  \centering
    \includegraphics[width=0.5\textwidth]{window3.png}
    \caption{window3}
\end{figure}

\begin{figure}[h]
\label{fig:window4}
  \centering
    \includegraphics[width=0.5\textwidth]{window4.png}
    \caption{window4}
\end{figure}

\begin{figure}[h]
\label{fig:window5}
  \centering
    \includegraphics[width=0.5\textwidth]{window5.png}
    \caption{window5}
\end{figure}
\end{document}
